
\section{Experience}

\outerlist{

\entrybig
	{\textbf{tripool}}{Taiwan}
	{Software Engineer}{Mar. 2023 --- Current}
\innerlist{
	\entry{\textbf{App Development:} Developing and maintaining published Flutter apps on both Android and iOS platforms.}
	\entry{\textbf{Backend Development:} Developing in-house web applications using Flask, MongoDB \& Redis.}
	\entry{\textbf{CI/CD:} Testing/Deploying using Docker and GitHub Actions.}
}

\entrybig
	{\textbf{Dayeh-Takashimaya Department Store}}{Taipei, Taiwan}
	{Software Engineer}{Nov. 2021 --- Dec. 2022}
\innerlist{
	\entry{\textbf{App Development:} Developing and maintaining published Flutter apps on both Android and iOS platforms.}
	\entry{\textbf{Backend Development:} Developing in-house web applications using Django \& Django Rest Framework.}
	\entry{\textbf{Continuous Integration:} Unit testing using Docker and GitLab CI/CD.}
}

\entrybig
	{\textbf{National Taiwan University}}{Taipei, Taiwan}
	{Full-Time Research Assistant}{Aug. 2019 --- July 2021}
\innerlist{
	\entry{\textbf{Programming:} Designed experiments using Python to interact with eye trackers and Elekta magnetoencephalography (MEG) systems.}
	\entry{\textbf{Analysis:} Analyzed data using parametric and nonparametric methods with R and Python.}
	\entry{\textbf{Data Collection:} Recruited participants, conducted experiments and organized data.}
	\entry{\textbf{Lab Management:} Maintained devices and managed administrative works.}
}

\entrybig
	{\textbf{National Taiwan University}}{Taipei, Taiwan}
	{Research and Teaching Assistant}{Sept. 2017 --- July 2019}
\innerlist{
	\entry{\textbf{Part-Time Research Assistant:} Language Development Laboratory}
	\entry{\textbf{Teaching Assistant:} Psychology \& Life: From a Fresh Start, Developmental Psychology, General Psychology}
}

\entrybig
	{\textbf{National Cheng Kung University}}{Tainan, Taiwan}
	{Research and Teaching Assistant}{Sept. 2016 --- July 2017}
\innerlist{
	\entry{\textbf{Part-Time Research Assistant:} Laboratory of Language Acquisition and Cognitive Development}
	\entry{\textbf{Teaching Assistant:} Eprime Programming and Psychology Instrument Applications}
}

}
